---
title: "Movement Metrics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This script is meant to calculate different movement metrics for deer GPS points. Bucks and does are run separately because of a difference in fix rate (1 hour for does, 2 hours for bucks). Additional information on some of the movement metric code can be found (here)[https://www.danaseidel.com/MovEco-R-Workshop/Materials/Day6/Behavioral_Analysis/]. 

# Install Packages & Load Libraries
```{r}
packages <- c('adehabitatHR','adehabitatLT','lubridate','plyr','rgeos','here','rgdal')

install_load <- function(packages){
     for (p in packages) {
          if (p %in% rownames(installed.packages())) {
               library(p, character.only=TRUE)
          } else {
               install.packages(p)
               library(p,character.only = TRUE)
          }
     }
}

install_load(packages)
```

# Establish functions for RT and T2R
Functions for calculating Mean return time and mean time to return for gps collar data. This function calculates these two movement metrics for an indivdiual and will later be placed into a forloop to calculate the metrics for all individuals in a ltraj object.f

Source functions can be found (here)[https://www.danaseidel.com/MovEco-R-Workshop/Materials/Day6/Syndromes/]. From site: 
Residence time = the number of hours the animal spends inside a circle of a given radius centered on each location without leaving the radius for more than a specified cut-off time

Time-to-return = the number of hours the animal spends beyond a specified cut-off time before its return to a circle of a given radius centered on each location

Adapted from van Moorter et al. 2015, Journal of Animal Ecology
```{r}
RTandT2R <- function(x, radius, maxt, units="hour", addinfo = F){
  fR <- function(x, dframe, radius, maxt, units=units){
    tmp <- dframe[c(x:nrow(dframe)),]
    dists <- sqrt((tmp$x - tmp$x[1])^2 + (tmp$y - tmp$y[1])^2)
    dists <- as.numeric(dists<=radius)
    ext <- which(dists[-length(dists)] > dists[-1])+1
    entr <-  which(dists[-length(dists)] < dists[-1])+1
    bts <- difftime(tmp$date[entr], tmp$date[ext[c(1:length(entr))]], units=units)    
    tmp1 <- as.numeric(difftime(tmp$date[ext[(as.numeric(bts)>maxt)][1]], tmp$date[1], units=units)) #first exit
    if (is.na(tmp1) & length(ext)>0) tmp1 <- as.numeric(difftime(tmp$date[ext[length(ext)]], tmp$date[1], units=units))  
    tmp2 <- as.numeric(difftime(tmp$date[entr[(as.numeric(bts)>maxt)][1]], tmp$date[1], units=units)) #first re-entry
    return(c(tmp1, tmp2))
  } 
  res <- data.frame(do.call(rbind, lapply(c(1:nrow(x)), fR, dframe=x, radius=radius, maxt=maxt, units=units)))
  names(res) <- c(paste("RT", radius, maxt, sep="_"), paste("T2R", radius, maxt, sep="_"))
  
  if (!addinfo) return(res)
  if (addinfo) {
    attributes(x)$infolocs <- cbind(attributes(x)$infolocs, res)
    return(x) 
  }
}
```


# Pre-fire Doe
```{r}
collars <- read.csv(here::here('Publication_Data','Collars','deer-gps-prefiredoe.csv')) #load in dataframe
collars$TimeStamp <- as.POSIXct((collars$TimeStamp), format = "%Y-%m-%d %H:%M:%S", origin = '1970-01-01', tz = "UTC") #Create date object from time stamp


## dt = number of minutes between successive steps (3600 seconds = 1 hour)
ltraj <- as.ltraj(collars[, c("Easting", "Northing")], date = as.POSIXct(collars$TimeStamp, format= "%Y-%m-%d %H:%M:%S", tz = "America/Los_Angeles"), id=collars$AnimalID) #create a ltraj object that allows us to more easily work with time series spatial data like GPS collar data
plot(ltraj) #quick check to view all collars
ltraj2 <- cutltraj(ltraj, criterion = "dt > (3600*24)") #removing points that are not exactly 1 hour apart in each of the deers tracks
df <- ld(ltraj)


refda<- strptime("00:00", "%H:%M", tz="UTC") 
ltraj3 <- setNA(ltraj, refda, 1, units = "hour")
ltraj4<- sett0(ltraj3, refda, 1, units = "hour")
is.regular(ltraj4) #check that they are all 1 hour apart


##Turn Angle Correlation
TAC <- matrix(ncol=1, nrow=length(ltraj4)) # create empty data frame to populate with for-loop
for(i in 1:length(ltraj4)){SA <- adehabitatLT::acfang.ltraj(ltraj4[i], which = "relative") #compute correlogram for angular and linear descriptors of a movement path
TAC[i,] <- 1/(SA[[1]][1,])} #Compute turn angle correlation
View(TAC) 

##RT & T2R
lres <- list()
for (j in 1:length(ltraj)){
  res <- ltraj4[[j]][,c("x","y","date")]
  meanDist<- mean(ltraj4[[j]][1:nrow(ltraj4[[j]])-1,"dist"], na.rm=T)
  rads <- c(meanDist) 
  maxts <- c(12) 
  params <- expand.grid(rads=rads, maxts=maxts)
  for (i in 1:nrow(params)){
    nams <- names(res)
    tmp <- RTandT2R(ltraj4[[j]], radius = params$rads[i], maxt=params$maxts[i], units="hour", addinfo = F)
    res <- cbind(res, tmp)
    names(res) <- c(nams, paste("RT", params$rads[i], params$maxts[i], sep="_"), paste("T2R", params$rads[i], params$maxts[i], sep="_"))
  }
  lres[[j]] <- res
}

meanRTs <- sapply(lapply(lres, "[[", 4), function(x) mean(x, na.rm=T))
meanRTs

meanT2Rs <- sapply(lapply(lres, "[[", 5), function(x) mean(x, na.rm=T))
meanT2Rs


##MNSD --> Must be calculated after R2N
id <- levels(as.factor(df$id))
MNSD <- matrix (ncol=1, nrow=length(id))
for ( i in 1: length(id)){
  NSD <- data.frame (MNSD = df$R2n[which(df$id==id[i])])
  MNSD[i,] <- sapply(NSD, function(x) max(NSD$MNSD, na.rm=TRUE))
}
MNSD

#Meters/Hour - Change the  number in the first bracket for each deer
##to change the collar number - dist/dt
# dt is seconds per hour
sumdist <- sum(ltraj4[[16]][[6]], na.rm = TRUE)
tot.hour <- nrow(ltraj4[[16]])
meters.hour <- sumdist/tot.hour

#Meters/Day
meters.day <- meters.hour*24
```

# Post-fire Doe
```{r}
collars <- read.csv(here::here('Publication_Data','Collars','deer-gps-postfiredoe.csv')) #load in datafram
collars$TimeStamp <- as.POSIXct((collars$TimeStamp), format = "%Y-%m-%d %H:%M:%S", origin = '1970-01-01', tz = "UTC") #Create date object from time stamp

## dt = number of minutes between successive steps (3600 seconds = 1 hour)
ltraj <- as.ltraj(collars[, c("Easting", "Northing")], date = as.POSIXct(collars$TimeStamp, format= "%Y-%m-%d %H:%M:%S", tz = "America/Los_Angeles"), id=collars$AnimalID) #create a ltraj object that allows us to more easily work with time series spatial data like GPS collar data
ltraj2 <- cutltraj(ltraj, criterion = "dt > (3600*24)") #removing points that are not exactly 1 hour apart in each of the deers tracks
df <- ld(ltraj)
plot(ltraj)

refda<- strptime("00:00", "%H:%M", tz="UTC") 
refda
ltraj3 <- setNA(ltraj, refda, 1, units = "hour")
ltraj4<- sett0(ltraj3, refda, 1, units = "hour")
is.regular(ltraj4) #check that they are all 1 hour apart



##Turn Angle Correlation
TAC <- matrix(ncol=1, nrow=length(ltraj4)) # create empty data frame to populate with for-loop
for(i in 1:length(ltraj4)){SA <- adehabitatLT::acfang.ltraj(ltraj4[i], which = "relative")
TAC[i,] <- 1/(SA[[1]][1,])}
View(TAC)

##RT & T2R
lres <- list()
for (j in 1:length(ltraj)){
  res <- ltraj4[[j]][,c("x","y","date")]
  meanDist<- mean(ltraj4[[j]][1:nrow(ltraj4[[j]])-1,"dist"], na.rm=T)
  rads <- c(meanDist) 
  maxts <- c(12) 
  params <- expand.grid(rads=rads, maxts=maxts)
  for (i in 1:nrow(params)){
    nams <- names(res)
    tmp <- RTandT2R(ltraj4[[j]], radius = params$rads[i], maxt=params$maxts[i], units="hour", addinfo = F)
    res <- cbind(res, tmp)
    names(res) <- c(nams, paste("RT", params$rads[i], params$maxts[i], sep="_"), paste("T2R", params$rads[i], params$maxts[i], sep="_"))
  }
  lres[[j]] <- res
}

meanRTs <- sapply(lapply(lres, "[[", 4), function(x) mean(x, na.rm=T))
meanRTs

meanT2Rs <- sapply(lapply(lres, "[[", 5), function(x) mean(x, na.rm=T))
meanT2Rs


##MNSD --> Must be calculated after R2N
id <- levels(as.factor(df$id))
MNSD <- matrix (ncol=1, nrow=length(id))
for ( i in 1: length(id)){
  NSD <- data.frame (MNSD = df$R2n[which(df$id==id[i])])
  MNSD[i,] <- sapply(NSD, function(x) max(NSD$MNSD, na.rm=TRUE))
}
MNSD

#Meters/Hour - Should just put in forloop but if not just change the first number in the bracket
##to change the collar number - dist/dt
sumdist <- sum(ltraj4[[16]][[6]], na.rm = TRUE)
tot.hour <- nrow(ltraj4[[16]])
sumdist/tot.hour

#Meters/Day
meters.day <- meters.hour*24
```


# Pre-fire Buck
```{r}
collars <- read.csv(here::here('Publication_Data','Collars','deer-gps-prefirebuck.csv')) #load in datafram
collars$TimeStamp <- as.POSIXct((collars$TimeStamp), format = "%Y-%m-%d %H:%M:%S", origin = '1970-01-01', tz = "UTC") #Create date object from time stamp

## dt = number of minutes between successive steps (3600 seconds = 1 hour)
ltraj <- as.ltraj(collars[, c("Easting", "Northing")], date = as.POSIXct(collars$TimeStamp, format= "%Y-%m-%d %H:%M:%S", tz = "America/Los_Angeles"), id=collars$AnimalID) #create a ltraj object that allows us to more easily work with time series spatial data like GPS collar data
ltraj2 <- cutltraj(ltraj, criterion = "dt > (3600*24)") #removing points that are not exactly 1 hour apart in each of the deers tracks
df <- ld(ltraj)
plot(ltraj)



refda<- strptime("00:00", "%H:%M", tz="UTC") 
refda
ltraj3 <- setNA(ltraj, refda, 2, units = "hour")
ltraj4<- sett0(ltraj3, refda, 2, units = "hour")
is.regular(ltraj4) #check that they are all 1 hour apart



##Turn Angle Correlation
TAC <- matrix(ncol=1, nrow=length(ltraj4)) # create empty data frame to populate with for-loop
for(i in 1:length(ltraj4)){SA <- adehabitatLT::acfang.ltraj(ltraj4[i], which = "relative")
TAC[i,] <- 1/(SA[[1]][1,])}
View(TAC)

##RT & T2R
lres <- list()
for (j in 1:length(ltraj)){
  res <- ltraj4[[j]][,c("x","y","date")]
  meanDist<- mean(ltraj4[[j]][1:nrow(ltraj4[[j]])-1,"dist"], na.rm=T)
  rads <- c(meanDist) 
  maxts <- c(12) 
  params <- expand.grid(rads=rads, maxts=maxts)
  for (i in 1:nrow(params)){
    nams <- names(res)
    tmp <- RTandT2R(ltraj4[[j]], radius = params$rads[i], maxt=params$maxts[i], units="hour", addinfo = F)
    res <- cbind(res, tmp)
    names(res) <- c(nams, paste("RT", params$rads[i], params$maxts[i], sep="_"), paste("T2R", params$rads[i], params$maxts[i], sep="_"))
  }
  lres[[j]] <- res
}

meanRTs <- sapply(lapply(lres, "[[", 4), function(x) mean(x, na.rm=T))
meanRTs

meanT2Rs <- sapply(lapply(lres, "[[", 5), function(x) mean(x, na.rm=T))
meanT2Rs


##MNSD --> Must be calculated after R2N
id <- levels(as.factor(df$id))
MNSD <- matrix (ncol=1, nrow=length(id))
for ( i in 1: length(id)){
  NSD <- data.frame (MNSD = df$R2n[which(df$id==id[i])])
  MNSD[i,] <- sapply(NSD, function(x) max(NSD$MNSD, na.rm=TRUE))
}
MNSD

#Meters/Hour -  change the first number in the bracket
##to change the collar number - dist/dt
sumdist <- sum(ltraj4[[2]][[6]], na.rm = TRUE)
tot.hour <- nrow(ltraj4[[2]])*2 # x2 for bucks because fix rate is every 2 hours
meters.hour <- sumdist/tot.hour

meters.day <- meters.hour*24

```


# Post-fire Buck
```{r}
collars <- read.csv(here::here('Publication_Data','Collars','deer-gps-postfirebuck.csv')) #load in dataframe
collars$TimeStamp <- as.POSIXct((collars$TimeStamp), format = "%Y-%m-%d %H:%M:%S", origin = '1970-01-01', tz = "UTC") #Create date object from time stamp

## dt = number of minutes between successive steps (3600 seconds = 1 hour)
ltraj <- as.ltraj(collars[, c("Easting", "Northing")], date = as.POSIXct(collars$TimeStamp, format= "%Y-%m-%d %H:%M:%S", tz = "America/Los_Angeles"), id=collars$AnimalID) #create a ltraj object that allows us to more easily work with time series spatial data like GPS collar data
ltraj2 <- cutltraj(ltraj, criterion = "dt > (3600*24)") #removing points that are not exactly 1 hour apart in each of the deers tracks
df <- ld(ltraj)
plot(ltraj)

refda<- strptime("00:00", "%H:%M", tz="UTC") 
refda
ltraj3 <- setNA(ltraj, refda, 2, units = "hour")
ltraj4<- sett0(ltraj3, refda, 2, units = "hour")
is.regular(ltraj4) #check that they are all 1 hour apart

##Turn Angle Correlation
TAC <- matrix(ncol=1, nrow=length(ltraj4)) # create empty data frame to populate with for-loop
for(i in 1:length(ltraj4)){SA <- adehabitatLT::acfang.ltraj(ltraj4[i], which = "relative")
TAC[i,] <- 1/(SA[[1]][1,])}
View(TAC)

##RT & T2R
lres <- list()
for (j in 1:length(ltraj)){
  res <- ltraj4[[j]][,c("x","y","date")]
  meanDist<- mean(ltraj4[[j]][1:nrow(ltraj4[[j]])-1,"dist"], na.rm=T)
  rads <- c(meanDist) 
  maxts <- c(12) 
  params <- expand.grid(rads=rads, maxts=maxts)
  for (i in 1:nrow(params)){
    nams <- names(res)
    tmp <- RTandT2R(ltraj4[[j]], radius = params$rads[i], maxt=params$maxts[i], units="hour", addinfo = F)
    res <- cbind(res, tmp)
    names(res) <- c(nams, paste("RT", params$rads[i], params$maxts[i], sep="_"), paste("T2R", params$rads[i], params$maxts[i], sep="_"))
  }
  lres[[j]] <- res
}

meanRTs <- sapply(lapply(lres, "[[", 4), function(x) mean(x, na.rm=T))
meanRTs

meanT2Rs <- sapply(lapply(lres, "[[", 5), function(x) mean(x, na.rm=T))
meanT2Rs


##MNSD --> Must be calculated after R2N
id <- levels(as.factor(df$id))
MNSD <- matrix (ncol=1, nrow=length(id))
for ( i in 1: length(id)){
  NSD <- data.frame (MNSD = df$R2n[which(df$id==id[i])])
  MNSD[i,] <- sapply(NSD, function(x) max(NSD$MNSD, na.rm=TRUE))
}
MNSD

#Meters/Hour -  change the first number in the bracket
##to change the collar number - dist/dt
sumdist <- sum(ltraj4[[1]][[6]], na.rm = TRUE)
tot.hour <- nrow(ltraj4[[1]])*2 # x2 for bucks because fix rate is every 2 hours
meters.hour <- sumdist/tot.hour

meters.day <- meters.hour*24
```