---
title: "T-tests"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

`%notin%` <- negate(`%in%`)
```

In this script, we run statistical tests to compare differences in movement metrics among deer in and outside of the fire perimeter, and for deer before vs. after the fire.

## Import data

The movement metric summary spreadsheet was created manually based on the results from the 01_Calculate_Movement_Metrics.Rmd script.
```{r}
table <- read.csv(here::here("Publication_Data","Derived","summary-movement-metrics.csv"))

# take various subsets of these deer based on location of home range in vs. out of fire, and sex
doe_all <- filter(table, AnimalID %notin% c("H3", "P4"))
doe_out <- filter(doe_all, AnimalID %in% c("A5b", "H4", "H5", "J5", "K4"))
doe_in <- filter(doe_all, AnimalID %notin% c("A5b", "H4", "H5", "J5", "K4"))

deer_in <- filter(table, AnimalID %notin% c("A5b", "H4", "H5", "J5", "K4"))
deer_out <- filter(table, AnimalID %in% c("A5b", "H4", "H5", "J5", "K4")) # same as doe_out (no bucks out)
```

## Displacement During Fire

Displacement distances were calculated in QGIS, based on MCP centroids as calculated in other scripts.
```{r}
# not equal variances use welches t test
var.test(deer_in$Distance, deer_out$Distance)

t.test(deer_in$Distance, deer_out$Distance, var.equal = FALSE) #t = 2.9707, df = 12.636, p-value = 0.0111

mean(deer_in$Distance)#avg = 1169.469, min = 42, max=4401
sd(deer_in$Distance)

mean(deer_out$Distance) #253.57
sd(deer_out$Distance)
```


Subsequent analyses done on does only, due to differences in buck metrics, and small sample sizes for bucks.

## Turn Angle Correlation

```{r}
#t=-0.54805, df=10, p=0.5957
t.test(doe$TAC_Paired_Pre,doe$TAC_Paired_Post, paired = T)

mean(doe_in$TAC_Paired_Pre)
sd(doe_in$TAC_Paired_Pre)
mean(doe_in$TAC_Paired_Post)
sd(doe_in$TAC_Paired_Post)

#t=0.60713, df=4, p=0.5765 
t.test(doe_out$TAC_Paired_Pre, doe_out$TAC_Paired_Post, paired=T)

mean(doe_out$TAC_Paired_Pre)
sd(doe_out$TAC_Paired_Pre)
mean(doe_out$TAC_Paired_Post)
sd(doe_out$TAC_Paired_Post)
```


## Mean Residence Time

```{r}
#t=-2.5105, df=10, p-value=0.03089
t.test(doe_in$MeanRT_Paired_Pre, doe_in$MeanRT_Paired_Post, paired=T)

mean(doe_out$MeanRT_Paired_Pre)
sd(doe_out$MeanRT_Paired_Pre)
mean(doe_out$MeanRT_Paired_Post)
sd(doe_out$MeanRT_Paired_Post)

#t=0.75316, df=4, p=0.4933
t.test(doe_out$MeanRT_Paired_Pre, doe_out$MeanRT_Paired_Post, paired=T)

mean(doe_out$MeanRT_Paired_Pre)
sd(doe_out$MeanRT_Paired_Pre)
mean(doe_out$MeanRT_Paired_Post)
sd(doe_out$MeanRT_Paired_Post)
```


## Mean Time to Return

```{r}
#t=2.0221, df=10, p-value =0.07073
t.test(doe_in$MeanT2r_Paired_Pre, doe_in$MeanT2R_Paired_Post, paired=T)

mean(doe_in$MeanT2r_Paired_Pre)
sd(doe_in$MeanT2r_Paired_Pre)
mean(doe_in$MeanT2R_Paired_Post)
sd(doe_in$MeanT2R_Paired_Post)

#t=-0.3235, df=4, p=0.7625
t.test(doe_out$MeanT2r_Paired_Pre, doe_out$MeanT2R_Paired_Post, paired=T)

mean(doe_out$MeanT2r_Paired_Pre)
sd(doe_out$MeanT2r_Paired_Pre)
mean(doe_out$MeanT2R_Paired_Post)
sd(doe_out$MeanT2R_Paired_Post)
```


## Daily Movement Distance

```{r}
#t = -5.6776, df = 10, p-value = 0.0002045
t.test(doe_in$Mean_Dist_Day_Paired_Pre, doe_in$Mean_Dist_Day_Paired_Post, paired=T)

mean(doe_in$Mean_Dist_Day_Paired_Pre)
sd(doe_in$Mean_Dist_Day_Paired_Pre)
mean(doe_in$Mean_Dist_Day_Paired_Post)
sd(doe_in$Mean_Dist_Day_Paired_Post)

#t=0.28159, df=4, p=0.7922
t.test(doe_out$Mean_Dist_Day_Paired_Pre, doe_out$Mean_Dist_Day_Paired_Post, paired=T)

mean(doe_out$Mean_Dist_Day_Paired_Pre)
sd(doe_out$Mean_Dist_Day_Paired_Pre)
mean(doe_out$Mean_Dist_Day_Paired_Post)
sd(doe_out$Mean_Dist_Day_Paired_Post)

```


## Straightness

```{r}
#t = -2.0564, df = 10, p-value = 0.06679
t.test(doe_in$Straightness_Paired_Pre, doe_in$Straightness_Paired_Post, paired=T)

mean(doe_in$Straightness_Paired_Pre)
sd(doe_in$Straightness_Paired_Pre)
mean(doe_in$Straightness_Paired_Post)
sd(doe_in$Straightness_Paired_Post)

#t=0.19225, df=4, p=0.8569
t.test(doe_out$Straightness_Paired_Pre, doe_out$Straightness_Paired_Post, paired=T)

mean(doe_out$Straightness_Paired_Pre)
sd(doe_out$Straightness_Paired_Pre)
mean(doe_out$Straightness_Paired_Post)
sd(doe_out$Straightness_Paired_Post)
```


## Home Range Size

```{r}
#t = -1.9658, df = 10, p-value = 0.07768
t.test(doe_in$HR_Paired_Pre, doe_in$HR_Paired_Post, paired=T)

mean(doe_in$HR_Paired_Pre)
sd(doe_in$HR_Paired_Pre)
mean(doe_in$HR_Paired_Post)
sd(doe_in$HR_Paired_Post)

#t= -1.4938, df=4, p = 0.2095
t.test(doe_out$HR_Paired_Pre, doe_out$HR_Paired_Post, paired=T)

mean(doe_out$HR_Paired_Pre)
sd(doe_out$HR_Paired_Pre)
mean(doe_out$HR_Paired_Post)
sd(doe_out$HR_Paired_Post)
```

