---
title: "MCP Generation"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This script creates MCP centroids for all deer pre and post fire

```{r}
packages <- c('adehabitatHR','adehabitatLT','lubridate','plyr','rgeos','here','rgdal', 'sp', 'dplyr','raster','proxy','tibble','stringr')

install_load <- function(packages){
     for (p in packages) {
          if (p %in% rownames(installed.packages())) {
               library(p, character.only=TRUE)
          } else {
               install.packages(p)
               library(p,character.only = TRUE)
          }
     }
}

install_load(packages)

`%notin%` <- Negate(`%in%`)
```

# Pre-fire Deer MCP and Centroids

## Pre-fire
```{r}
# This script was used to generate MCPs
prefire <- read.csv(here::here("Publication_Data","Collars","deer-gps-prefire.csv")) #load in pre-fire dataframe

# Create SPDF
prefire.spdf <- SpatialPointsDataFrame(coords=as.data.frame(cbind(prefire$Easting, prefire$Northing)), 
                                       data=prefire,
                                       proj4string=CRS("+proj=utm +zone=10 ellps=WGS84")) #create spatial points dataframe

# Calculate MCP
prefire.mcp <- mcp(prefire.spdf[,"AnimalID"], percent=95, unin="m", unout="km2") # create 95% mcp for each animal in km^2
plot(prefire.mcp, col=c(1:length(unique(prefire$AnimalID))))  #show plot of all deer mcps

trueCentroidsPre <- as.data.frame(gCentroid(prefire.mcp, byid=TRUE)) # get centroid of each mcp
trueCentroidsPre$Time <- 'Pre'
```

## Post-fire
```{r}
postfire <- read.csv(here::here("Publication_Data","Collars","deer-gps-postfire.csv")) #load in pre-fire dataframe

# Remove J3 'during fire' points from home range analysis (due to high displacement) 
postfire <- postfire[-c(5715:5768),]

# Create SPDF
postfire.spdf <- SpatialPointsDataFrame(coords=as.data.frame(cbind(postfire$Easting, postfire$Northing)), 
                                       data=postfire,
                                       proj4string=CRS("+proj=utm +zone=10 ellps=WGS84")) #create spatial points dataframe

# Calculate MCP
postfire.mcp <- mcp(postfire.spdf[,"AnimalID"], percent=95, unin="m", unout="km2") # create 95% mcp for each animal in km^2
plot(postfire.mcp, col=c(1:length(unique(postfire$AnimalID))))  #show plot of all deer mcps

trueCentroidsPost <- as.data.frame(gCentroid(postfire.mcp, byid=TRUE)) # get centroid of each mcp
trueCentroidsPost$Time <- 'Post'
```


# All Centroids
Merge all centroids to create dataframe of centroid locations
```{r}
all.centroids <- bind_rows(trueCentroidsPre, trueCentroidsPost) # combine the 2 dataframes
all.centroids <- all.centroids[order(rownames(all.centroids)),] #order by rowname (animal id)
all.centroids <- all.centroids[order(all.centroids$Time),]# order by time period

# create column for ID - requires some weird formatting fixes
all.centroids$AnimalID <- row.names(all.centroids)
all.centroids$AnimalID <- substr(all.centroids$AnimalID, start = 1, stop = 2)

# fix the three-character deer
all.centroids$AnimalID <- as.factor(all.centroids$AnimalID)
levels(all.centroids$AnimalID)[levels(all.centroids$AnimalID)=="A5"] ="A5b"
levels(all.centroids$AnimalID)[levels(all.centroids$AnimalID)=="D3"] ="D3b"

head(all.centroids)
#write.csv(all.centroids, here::here('Publication_Data','Collars','MCP_Centroid.csv'), row.names = F)
```


# Calculate distances between pre and post fire centroids

```{r}
pre_centroids <- as.data.frame(trueCentroidsPre) %>% 
  dplyr::select(-Time)
post_centroids <- as.data.frame(trueCentroidsPost) %>% 
  dplyr::select(-Time)

#creates distance between centroid matrix
distmatrix <- proxy::dist(pre_centroids, post_centroids, method="euclidean")

#extract just diagnol from matrix
distances <- diag(distmatrix) %>% 
  as.data.frame() %>% 
  dplyr::rename(distances, Distance = `.`) %>% 
  rownames_to_column("AnimalID")

# subset
distances_doein <- distances %>% 
  filter(AnimalID %notin% c("A5b", "H4", "H5", "J5", "K4", "H3", "P4")) # remove 2 bucks and 5 does outside

distances_doeout <- distances %>% 
  filter(AnimalID %in% c("A5b", "H4", "H5", "J5", "K4")) # take only 5 does outside fire

mean(distances_doein$Distance) # 140.3179
sd(distances_doein$Distance) # 67.97086

mean(distances_doeout$Distance) # 119.2079
sd(distances_doeout$Distance) # 108.3689

t.test(distances_doein$Distance, distances_doeout$Distance, paired=F) 
# t = 0.40119, df = 5.4883, p = 0.7034
```


# Calculate distance moved DURING fire

Using the files 'far.csv' and 'MCP_Centroids.csv' (found in 'Collars' under 'Publication_Data') and created above, we created a distance matrix in QGIS. To do this, we filtered the MCP centroids to only pre-fire homerange centroids and used the 'distance matrix' function in base QGIS. 

```{r}
distances <- read.csv(here::here("Publication_Data",'Collars','distances.csv'))
(distances.same.deer <- distances[c(distances$TargetID==distances$InputID),])
#write.csv(distances.same.deer,'Distances_During_Fire_QGIS.csv')
```