---
title: "Deer RSF Pre and Post Fire"
author: "Kaitlyn"
date: "5/28/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = F, warning = F, error = FALSE)
```

### Set up, import data

```{r}
library(lme4)
library(MuMIn)
library(caret)
library(ROCR)
library(tidyverse)
library(raster)
library(rgdal)
library(car)
```


Read in dataframe and filter by time period.

This dataframe includes rows for used points and randomly-generated points, and associated values of landscape covariates as extracted from underlying raster layers. All data have already been centered and scaled for modeling.

```{r}
all_data <- read.csv("Publication_Data/Collars/RSF_input.csv") 

PreAll <- filter(all_data, Period == "Pre") 
PostAll <- filter(all_data, Period == "Post") 
```



### Model Selection

#### Pre-Fire Models

Backwards step-wise model selection based on AIC.

```{r, eval = F}
(PreNull <- glmer(Case ~ (1|AnimalID), family = "binomial", data = PreAll))                                                                                     # 30303.20

(PreFull <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))    # 30107.17
  
# stepping backward from full model
(PreModel1.1 <- glmer(Case ~ elevation + slope + east + north + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))      #  30123.08
(PreModel1.2 <- glmer(Case ~ veg + slope + east + north + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))            # 30140.95
(PreModel1.3 <- glmer(Case ~ veg + elevation + east + north + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))        # 30166.65
(PreModel1.4 <- glmer(Case ~ veg + elevation + slope + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))                             # 30163.71
(PreModel1.5 <- glmer(Case ~ veg + elevation + slope + east + north + water + Sex + (1|AnimalID), family = "binomial", data = PreAll))           # 30110.71
(PreModel1.6 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + Sex + (1|AnimalID), family = "binomial", data = PreAll))         # 30118.21
(PreModel1.7 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + (1|AnimalID), family = "binomial", data = PreAll))      # 30105.61 - best of this batch (no Sex)

# stepping backwards from PreModel1.7 - none improve on 1.7, still the best
(PreModel2.1 <- glmer(Case ~ elevation + slope + east + north + rugged + water + (1|AnimalID), family = "binomial", data = PreAll)) # 30121.54
(PreModel2.2 <- glmer(Case ~ veg + slope + east + north + rugged + water + (1|AnimalID), family = "binomial", data = PreAll)) # 30138.98 *
(PreModel2.3 <- glmer(Case ~ veg + elevation + east + north + rugged + water + (1|AnimalID), family = "binomial", data = PreAll)) # 30165.17
(PreModel2.4 <- glmer(Case ~ veg + elevation + slope + rugged + water + (1|AnimalID), family = "binomial", data = PreAll)) # 30162.46
(PreModel2.5 <- glmer(Case ~ veg + elevation + slope + east + north + water + (1|AnimalID), family = "binomial", data = PreAll)) # 30109.23
(PreModel2.6 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + (1|AnimalID), family = "binomial", data = PreAll)) # 30116.76

vif(PreModel1.7) # check VIF
summary(PreModel1.7)
```


#### Post-Fire Models

Same as above, but with surviving vegetation predictor as well.

```{r, eval = F}
(PostNull <- glmer(Case ~ (1|AnimalID), family = "binomial", data = PostAll))                                                                            # 27762.54

(PostFull <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26152.42
vif(PostFull)

# stepping backward from full model
(PostModel1.1 <- glmer(Case ~ elevation + slope + east + north + rugged + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26761.53
(PostModel1.2 <- glmer(Case ~ veg + slope + east + north + rugged + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26191.72
(PostModel1.3 <- glmer(Case ~ veg + elevation + east + north + rugged + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26160.10
(PostModel1.4 <- glmer(Case ~ veg + elevation + slope + rugged + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26213.70
(PostModel1.5 <- glmer(Case ~ veg + elevation + slope + east + north + water + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26262.57
(PostModel1.6 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + survveg.3 + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26163.90
(PostModel1.7 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + Sex + (1|AnimalID), family = "binomial", data = PostAll)) # 26568.19
(PostModel1.8 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26150.56 # the best of the bunch, with all variables except Sex

# stepping backwards from PostModel1.8 - none improve on 1.8, still the best
(PostFull2.1 <- glmer(Case ~ elevation + slope + east + north + rugged + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26759.72
(PostFull2.2 <- glmer(Case ~ veg + slope + east + north + rugged + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26189.99
(PostFull2.3 <- glmer(Case ~ veg + elevation + east + north + rugged + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26158.23
(PostFull2.4 <- glmer(Case ~ veg + elevation + slope + rugged + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26211.79
(PostFull2.5 <- glmer(Case ~ veg + elevation + slope + east + north + water + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26260.66
(PostFull2.6 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + survveg.3 + (1|AnimalID), family = "binomial", data = PostAll)) # 26162.02
(PostFull2.7 <- glmer(Case ~ veg + elevation + slope + east + north + rugged + water + (1|AnimalID), family = "binomial", data = PostAll)) # 26566.35

vif(PostModel1.8) # check VIF
summary(PostModel1.8)
```


### Model validation

Area-adjusted cross-validation of models, as described in manuscript.

Read in raster stacks, masked to study areas, for validation. (NOTE: We did not include these raster layers here, but if you are interested in the data or in how we ran this validation, please get in touch.)
```{r}
# bring in the individual raster stacks cropped to each deer's home range
individual_stacks <- list()
for (i in 1:13) {
  
  file_name <- paste("individual_rasters/Stack_",
                     levels(all_data$AnimalID)[i], ".grd", sep = "")
  
  individual_stacks[[i]] <- stack(file_name)
}

names(individual_stacks) <- levels(all_data$AnimalID)
```

Store factor levels in list (needed for predicting the model with the raster stack in validation)
```{r}
survveg.3.levels <- list(levels(all_data$survveg.3))
names(survveg.3.levels) <- "survveg.3"
```


#### Pre-Fire

```{r, echo = F}
set.seed(15)

simulations <- list()

nsim <- 100

for(j in 1:13) { # loop through the 13 individual deer

  for (i in 1:nsim){ # repeat for nsim iterations
    
    traintest <- PreAll %>%
      filter(AnimalID == names(individual_stacks[j])) %>% # filter for only that deer
      dplyr::mutate(n = row_number()) %>% #create row number if you dont have one
      dplyr::select(n, everything()) # put 'n' at the front of the dataset
  
    training <- traintest %>%
      group_by(Case) %>% # any number of variables you wish to partition by proportionally
      sample_frac(.8) # '.8' is the proportion of the original df you wish to sample
  
    testing <- anti_join(traintest, training) # creates test dataframe with those observations not in 'train.'
    
    test.model<- glm(Case ~ veg + elevation + slope + east + north + rugged + water, 
                       family="binomial",
                       data = training)
  
    testing$predict1 <- predict(test.model, testing, type="response")
    
    # needed to add line re.form = ~0 since there are no "random effects" when just predicting spatially
    rastpredict <- predict(individual_stacks[[j]], test.model, 
                           allow.new.levels=T, type="response", re.form=~0,
                           factors = veg.levels) 
    
    testingsub <- subset(testing,Case==1)
    
    quantpredict <- data.frame(quantile(testingsub$predict1,probs=c(seq(0,1,by=0.1))))
    
    binbreaks<-c(quantpredict[,1])
    binbreaks[1]<-0
    binbreaks[11]<-1
    
    reclass_df <- t(matrix(c(binbreaks[1:10],binbreaks[2:11],seq(1:10)),ncol=10,byrow=T))
    r1.class <- reclassify(rastpredict,reclass_df)
    r1.area<-data.frame(freq(r1.class))
    r1.area<-r1.area[-11,]
    r1.areas<-r1.area$count/sum(r1.area$count)
    
    testingsub$predictbins<-.bincode(testingsub$predict1,breaks=binbreaks)
    
    # to prevent error message in case of bin issue
    if(length((table(testingsub$predictbins)/sum(table(testingsub$predictbins)))) != length(r1.areas)) {
      
      simulations[[(nsim*(j-1) + i)]] <- NA
      
    } else {
          
        area.adjust<-data.frame(((table(testingsub$predictbins)/sum(table(testingsub$predictbins))))/r1.areas)
        
        area.adjust$AnimalID <- j
        
        simulations[[(nsim*(j-1) + i)]]<-area.adjust
    
    }

  }
}

simulations.all<-do.call(rbind, simulations)

simulations.all<-data.frame(simulations.all)

library(plyr)
kfold.ply<-ddply(simulations.all,.(Var1, AnimalID),summarize,mean=mean(Freq),sd=sd(Freq),count=length(Freq))

kfold.ply$se<-kfold.ply$sd/sqrt(kfold.ply$count)

kfold.ply$Var2<-as.numeric(kfold.ply$Var1)


# run correlation tests for each individual animal
cor.test.list <- list()
for(i in 1:13) {
  cor.test.list[[i]] <-
  cor.test(~mean+Var2,
         data = filter(kfold.ply, AnimalID == i),
         method = "spearman")
}

cor.test.list

#maxy<-max(kfold.ply$mean)+10*max(kfold.ply$se)

ggplot(kfold.ply, aes(x=Var1, y=mean,group=1)) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  theme_classic()+
  xlab("Binned RSF Score")+ylab("Area Adjusted Frequency")+
  ggtitle("Pre Fire") +
  geom_line() +  geom_point(size=2.5)+ 
 # ylim(0,maxy)+
  geom_hline(yintercept=1, linetype="dashed",size=1.5) +
  facet_wrap(~AnimalID, scales = "free")


## for all individuals combined

kfold.ply.all <- ddply(simulations.all,.(Var1),summarize,mean=mean(Freq),sd=sd(Freq),count=length(Freq))

kfold.ply.all$se<-kfold.ply.all$sd/sqrt(kfold.ply.all$count)

kfold.ply.all$Var2<-as.numeric(kfold.ply.all$Var1)

# run for all individuals combined
cor.test(~mean+Var2,
       data = kfold.ply.all,
       method = "spearman")

ggplot(kfold.ply.all, aes(x=Var1, y=mean,group=1)) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  theme_classic()+
  xlab("Binned RSF Score")+ylab("Area Adjusted Frequency")+
  ggtitle("Pre Fire") +
  geom_line() +  geom_point(size=2.5)+ 
 # ylim(0,maxy)+
  geom_hline(yintercept=1, linetype="dashed",size=1.5)
```


#### Post-Fire

```{r, echo = F}
set.seed(5)

simulations <- list()

nsim <- 100

for(j in 1:13) { # loop through the 13 individual deer

  for (i in 1:nsim){ # repeat for nsim iterations
    
    traintest <- PostAll %>%
      filter(AnimalID == names(individual_stacks[j])) %>% # filter for only that deer
      dplyr::mutate(n = row_number()) %>% #create row number if you dont have one
      dplyr::select(n, everything()) # put 'n' at the front of the dataset
  
    training <- traintest %>%
      group_by(Case) %>% # any number of variables you wish to partition by proportionally
      sample_frac(.8) # '.8' is the proportion of the original df you wish to sample
  
    testing <- anti_join(traintest, training) # creates test dataframe with those observations not in 'train.'
    
    test.model<- glm(Case ~ veg + elevation + slope + east + north + rugged + water + survveg.3, 
                     family="binomial",
                     data = training)
  
    testing$predict1 <- predict(test.model, testing, type="response")
    
    # needed to add line re.form = ~0 since there are no "random effects" when just predicting spatially
    rastpredict <- predict(individual_stacks[[j]], test.model, 
                           allow.new.levels=T, type="response", re.form=~0,
                           factors = c(veg.levels, survveg.3.levels)) 
    
    testingsub <- subset(testing,Case==1)
    
    quantpredict <- data.frame(quantile(testingsub$predict1,probs=c(seq(0,1,by=0.1))))
    
    binbreaks<-c(quantpredict[,1])
    binbreaks[1]<-0
    binbreaks[11]<-1
    
    reclass_df <- t(matrix(c(binbreaks[1:10],binbreaks[2:11],seq(1:10)),ncol=10,byrow=T))
    r1.class <- reclassify(rastpredict,reclass_df)
    r1.area<-data.frame(freq(r1.class))
    r1.area<-r1.area[-11,]
    r1.areas<-r1.area$count/sum(r1.area$count)
    
    testingsub$predictbins<-.bincode(testingsub$predict1,breaks=binbreaks)
    
    # to prevent error message in case of bin issue
    if(length((table(testingsub$predictbins)/sum(table(testingsub$predictbins)))) != length(r1.areas)) {
      
      simulations[[(nsim*(j-1) + i)]] <- NA
      
    } else {
          
        area.adjust<-data.frame(((table(testingsub$predictbins)/sum(table(testingsub$predictbins))))/r1.areas)
        
        area.adjust$AnimalID <- j
        
        simulations[[(nsim*(j-1) + i)]]<-area.adjust
    
    }
  }
}

simulations.all<-do.call(rbind, simulations)

simulations.all<-data.frame(simulations.all)

library(plyr)
kfold.ply<-ddply(simulations.all,.(Var1, AnimalID),summarize,mean=mean(Freq),sd=sd(Freq),count=length(Freq))

kfold.ply$se<-kfold.ply$sd/sqrt(kfold.ply$count)

kfold.ply$Var2<-as.numeric(kfold.ply$Var1)


# run correlation tests for each individual animal
cor.test.list <- list()
for(i in 1:13) {
  cor.test.list[[i]] <-
  cor.test(~mean+Var2,
         data = filter(kfold.ply, AnimalID == i),
         method = "spearman")
}

cor.test.list

#maxy<-max(kfold.ply$mean)+10*max(kfold.ply$se)

ggplot(kfold.ply, aes(x=Var1, y=mean,group=1)) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  theme_classic()+
  xlab("Binned RSF Score")+ylab("Area Adjusted Frequency")+
  ggtitle("Post Fire") +
  geom_line() +  geom_point(size=2.5)+ 
 # ylim(0,maxy)+
  geom_hline(yintercept=1, linetype="dashed",size=1.5) +
  facet_wrap(~AnimalID, scales = "free")


## for all individuals combined

kfold.ply.all <- ddply(simulations.all,.(Var1),summarize,mean=mean(Freq),sd=sd(Freq),count=length(Freq))

kfold.ply.all$se<-kfold.ply.all$sd/sqrt(kfold.ply.all$count)

kfold.ply.all$Var2<-as.numeric(kfold.ply.all$Var1)

# run for all individuals combined
cor.test(~mean+Var2,
       data = kfold.ply.all,
       method = "spearman")

ggplot(kfold.ply.all, aes(x=Var1, y=mean,group=1)) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.1) +
  theme_classic()+
  xlab("Binned RSF Score")+ylab("Area Adjusted Frequency")+
  ggtitle("Post Fire") +
  geom_line() +  geom_point(size=2.5)+ 
 # ylim(0,maxy)+
  geom_hline(yintercept=1, linetype="dashed",size=1.5)
```
